The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-08-14 ms/ms.tex
add text

\section{Experiment Description}
\label{methods}
\subsection{Model description}
\label{sect:md}
The is developed by the CESM Land Model Working Group and maintained at the National Center for Atmospheric Research (NCAR). This experiment utilizes the Community Land Model configuration version 5.1 (CLM5.1) of the Community Terrestrial Systems Model. The model source code and documentation are available online (\url{https://github.com/ESCOMP/CTSM}), as is a full model description \cite{lawrence2019}.

@@

The PPE is likewise useful for determining which parameters influence which model processes and where. For example the parameters controlling leaf area index vary significantly by biome (Figure \ref{fig:lai}). Plant hydraulics parameters were the most important in the tropical rain forest, photosynthetic capacity in the boreal forest, and runoff and soil evaporation in the temperate grassland/desert biome. The most influential parameters globally include parameters that were important in each of these three biomes. Because the number of potential variables, parameters, and geographical ranges of interest to the wider CLM community is larger than we can document here,  we provide a tool that can be used to explore an extended diagnostics set which summarises the $>$2TB of output data and contains 1720 figures (\url{https://webext.cgd.ucar.edu/I2000/PPEn11_OAAT}).

@@

In many cases we found it easier to utilize interactive plotting utilities to toggle through the various parameters, output variables, and forcing scenarios (Figure \ref{fig:panel}). Interactive widgets are relatively easy to generate within a data analysis session, but more difficult to host online, hence the screenshot.

>>>>

\section{Experiment Description}
\label{methods}
\subsection{Model description}
\label{sect:md}
This experiment utilizes the Community Land Model configuration version 5.1 (CLM5.1) of the Community Terrestrial Systems Model. The model source code and documentation are available online (\url{https://github.com/ESCOMP/CTSM}), as is a full model description \cite{lawrence2019}.

@@

The PPE is likewise useful for determining which parameters influence which model processes and where. For example the parameters controlling leaf area index vary significantly by biome (Figure \ref{fig:lai}). Plant hydraulics parameters were the most important in the tropical rain forest, photosynthetic capacity in the boreal forest, and runoff and soil evaporation in the temperate grassland/desert biome. The most influential parameters globally include parameters that were important in each of these three biomes.

@@

Because the number of potential variables, parameters, and geographical ranges of interest to the wider CLM community is larger than we can document here,  we provide a tool that can be used to explore an extended diagnostics set which summarises the $>$2TB of output data via approximately 2000 plots (\url{https://webext.cgd.ucar.edu/I2000/PPEn11_OAAT}).

The diagnostics website includes ranking plots (as in Figure \ref{fig:lai}) and maps of parameter effects (as in Figure \ref{fig:panel}). But these plots are repeated across a combination of model output variables and model parameters. Likewise figures are repeated for each of the various forcing scenarios.
